---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

Interactivity plots in ploty 
```{r include=FALSE}
library(tidyverse)
library(p8105.datasets)

library(dplyr)
library(plotly)
library(stringr)
library(forcats)
```


```{r include=FALSE}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)

```



# Plotly Scatterplot of NYC Airbnb Data

Using plotly to make some quick plots:
Same thought process as ggplot. 

- Start with a dataset 
- define aesthetics and go from there 
- to make a scatter plot you need to define plotly( mode = "markers")
- you can do things with strings 

```{r echo=TRUE}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |> 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```


# Plotly Boxplot of NYC Airbnb Data

To make a boxplot, you need to set type = "box"
You can hover over each box to see neighborhood name 
```{r echo=TRUE}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, 
          y = ~n, color = ~neighbourhood, 
          type = "bar", 
          colors = "viridis")
```



# Plotly Bar plot of NYC Resturant Data

```{r}
data("rest_inspec")
rest_inspec =
  rest_inspec|>
  filter(grade %in% c("A", "B", "C"), boro != "Missing") |> 
  mutate(boro = str_to_title(boro))

rest_inspec|> 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) |>
  group_by(boro) |>
  summarise(n = n(), .groups = 'drop') |>
  mutate(boro = fct_infreq(boro))|>
  plot_ly(x = ~boro, 
          y = ~n, color = ~boro, 
          type = "bar", 
          colors = "viridis")|>
  layout(title = "Pizza Places by Borough",
         xaxis = list(title = "Borough"),
         yaxis = list(title = "Number of Pizza Places"))

```


# Plotly Scatter plot of NYC Resturants Data

```{r}
rest_inspec|> 
  mutate(
    boro = str_to_title(boro))|>
  group_by(dba, boro) |>
  summarize(
    avg_score = mean(score, na.rm = TRUE),
    n_inspections = n()
  ) |>
  ungroup()|>
  plot_ly(y = ~n_inspections,
          x = ~avg_score, color = ~boro,
          type = "scatter",mode = "markers",
          colors = "viridis")|>
  layout(title = "Average Inspection Score and Number of Inspections by each Borough")
```

# Plotly Boxplot of NYC Resturant Data 

```{r}
rest_inspec|>
  plot_ly(x = ~boro,
          y = ~score, color = ~boro,
          type = "box",
          colors = "viridis")|>
  layout(
    title = "Distribution of Inspection Scores for each NYC Borough",
    xaxis = list(title = "Borough"),
    yaxis = list(title = "Inspection Scores")
  )
  
```
 
 
 

