---
title: "Plotly"
author: "Kimberly Lopez"
date: "2024-10-22"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
--- 
Interactivity plots in ploty 
```{r include=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```


```{r include=FALSE}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)

```


# Here are some plots 


# Plotly Scatterplot

Using plotly to make some quick plots 
Same thought process as ggplot. 

- Start with dataset 
- define aesthetics and go from there 
- to make a scatterplot you need to define plotly( mode = "markers")
- you can do things with strings 

```{r echo=TRUE}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |> 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

# Boxplot 

To make a boxplot, you need to set type = "box"
You can hover over each box to see neighborhood name 
```{r echo=TRUE}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, 
          y = ~n, color = ~neighbourhood, 
          type = "bar", 
          colors = "viridis")
```

Now do a barchart with number of rentals. 
To do this we need to create a count variable 
